Assessing the Accessibility of Protein Tunnels using Motion Planning

### 2017-12-06 paper.tex
color map included in last image
added Ondra

\author{Vojt\v ech Von\' asek$^{1}$,
    Barbora Kozl\'\i kov\'a$^{2}$,
    Adam Jur\v{c}\'\i k$^{2}$,
    Martin Saska$^{1}$
\thanks{$^{1}$ Faculty of Electrical Engineering,  Czech Technical University in Prague, 
Technick\'a 2, 166 27 Prague, Czech Republic,
{\tt vonasek@labe.felk.cvut.cz}}
\thanks{$^{2}$        
Faculty of Informatics, Masaryk University, Botanick\'a 68a, 602~00 Brno, Czech Republic,
%The presented work has been supported by the Czech Science Foundation (GA{\v C}R) under research project No. 17-07690S.
%Access to computing and storage facilities owned by parties and projects contributing to the National Grid Infrastructure MetaCentrum, provided under the programme "Projects of Large Infrastructure for Research, Development, and Innovations" (LM2010005), is greatly appreciated.
%}%
}
}

@@

\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{fig/dcp-image1Label}\\
\includegraphics[width=0.2\textwidth]{fig/colormap}
\caption{\label{fig::dcp}
Visualization of trajectories for the ligand DCP in the two examined tunnels.  
The color of the trajectories corresponds to the scale, that was needed to pass the given part of the tunnel.
The ligand can enter the first tunnel with a high scale (almost 1=100~\%) (A), but then it has to be scaled-down (to $\sim75$~\%) to pass the
next part of the tunnel (B). After this narrow passage, the tunnel is larger again and the ligand can traverse to the narrow passage with
scale $>75$~\% (C).
The second tunnel can also be entered with the high scale (green), but then the narrow part is traversable only with a low scale ($\sim50$~\%) (D). 
For the purpose of the visualization, even more scale-down to 0.3=30~\% was allowed (E) to see how the ligand passed the tunnel.
However, the ligand can reach the active site only with very low scale ($\sim0.4=40$~\%) using the side tunnel.
}
\end{figure}

>>>>

\author{Vojt\v ech Von\' asek$^{1}$,
    Barbora Kozl\'\i kov\'a$^{2}$,
    Adam Jur\v{c}\'\i k$^{2}$,
    Ond\v{r}ej V\'{a}vra$^{3}$,
    Martin Saska$^{1}$
\thanks{$^{1}$ Faculty of Electrical Engineering,  Czech Technical University in Prague, 
Technick\'a 2, 166 27 Prague, Czech Republic,
{\tt vonasek@labe.felk.cvut.cz}}
\thanks{$^{2}$        
Faculty of Informatics, Masaryk University, Botanick\'a 68a, 602~00 Brno, Czech Republic}
\thanks{$^{3}$        
Faculty of Informatics, Masaryk University, Botanick\'a 68a, 602~00 Brno, Czech Republic}
%The presented work has been supported by the Czech Science Foundation (GA{\v C}R) under research project No. 17-07690S.
%Access to computing and storage facilities owned by parties and projects contributing to the National Grid Infrastructure MetaCentrum, provided under the programme "Projects of Large Infrastructure for Research, Development, and Innovations" (LM2010005), is greatly appreciated.
%}%
%}
}

@@

\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{fig/dcp-image1Label}\\
%\includegraphics[width=0.2\textwidth]{fig/colormap}
\caption{\label{fig::dcp}
Visualization of trajectories for the ligand DCP in the two examined tunnels.  
The color of the trajectories corresponds to the scale, that was needed to pass the given part of the tunnel.
The ligand can enter the first tunnel with a high scale (almost 1=100~\%) (A), but then it has to be scaled-down (to $\sim75$~\%) to pass the
next part of the tunnel (B). After this narrow passage, the tunnel is larger again and the ligand can traverse to the narrow passage with
scale $>75$~\% (C).
The second tunnel can also be entered with the high scale (green), but then the narrow part is traversable only with a low scale ($\sim50$~\%) (D). 
For the purpose of the visualization, even more scale-down to 0.3=30~\% was allowed (E) to see how the ligand passed the tunnel.
However, the ligand can reach the active site only with very low scale ($\sim0.4=40$~\%) using the side tunnel.
}
\end{figure}
